How Well Do Strike Rates Translate from T20 to ODI Formats for Top 100 vs. Non-Top 100 players?

### 2024-12-03 paper/paper.qmd
donwload data, raw data, and simulate data

---
title: "Predicting Goodreads Ratings Across Genres"
subtitle: "My subtitle if needed"
author: 
  - Dhruv Gupta
thanks: "Code and data are available at: https://github.com/dhruv5423/GoodReads-Cross-Genre-Predictions"
date: today
date-format: long
toc: true
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

Goodreads, founded in 2006, boasts over 150 million users and is perhaps the most popular online community for4 readers. At it's heart, Goodreads is akin to a reader's social media platform, allowing them to display, discover, review, and catalog books they love (or hate) across multiple different genres.

>>>>

---
title: "How Well Do Strike Rates Translate from T20 to ODI Formats for Top 100 vs. Non-Top 100 players?"
subtitle: "My subtitle if needed"
author: 
  - Dhruv Gupta
thanks: "Code and data are available at: https://github.com/dhruv5423/Top-100-Batters-T20-to-ODI-Strike-Rate-Mapping"
date: today
date-format: long
toc: true
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

@@
